---
title: "Amplicon Coverage"
params:
  analysisDirFP: null
  runID: null
  seqDirFP: null
  pacbamDir: "pacbam"
  pacbamFileSuffix: ".primertrim.sorted.pileup"
  ampBED: null
  ampMinCov: 30
  ampMeanCov: 100
  ampMaxNFail: 5
  ampMinNPass: 93
---

```{r ampliconCov-comments, include=FALSE}
# There's still a lot of clean up and optimization to be done on this file. Big loops need to be broken up, repeated blocks put into functions, etc. 
# Note that turning on cache in block amp_cov is useful when testing on single run, but you have to turn it off when running operationally and delete any _cache directories.
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(formattable)
library(DT)
# stop summarise messages https://rstats-tips.net/2020/07/31/get-rid-of-info-of-dplyr-when-grouping-summarise-regrouping-output-by-species-override-with-groups-argument/
options(dplyr.summarise.inform = FALSE)
# Note that Rmd files use the location of the Rmd file as their working directory during knitting. This causes problems when trying to unambiguously locate external dependencies that aren't in the same directory. Setting working directory below to address.
knitr::opts_knit$set(root.dir = params$analysisDirFP)
```

#### Per Amplicon Coverage Summary
The table below lists the number of amplicons per sample or control with coverage statistics passing or failing coverage thresholds. To pass, amplicons must have an average depth of coverage of >= `r params$ampMeanCov`x across their length and a minimum coverage of >= `r params$ampMinCov`x at all nucleotide positions. Samples are listed in the first table and controls in the second. Desirable values are highlighted in green (>= `r params$ampMinNPass`/98 amplicons passing for samples, <= `r params$ampMaxNFail`/98 amplicons passing for controls) and undesirable values in bold red (> `r params$ampMaxNFail`/98 amplicons failing for samples, < `r params$ampMinNPass`/95 amplicons failing for controls). The report column links to detailed plots of the coverage for each amplicon for a given sample or control.

```{r read_bed, include=FALSE}
# read in the amplicon bed file to get the amplicon coordinates
ampInfo <- read_tsv(params$ampBED, col_names = FALSE)
colnames(ampInfo) <- c("REF", "START", "END", "AMP_ID", "POOL", "TRASH")
ampInfo <- select(ampInfo, -TRASH, -REF)
```
```{r amp_cov, include=FALSE}
# Read in the names of all of the files; note cache=TRUE for this block because it takes a long time to read everything in.
pbFiles <- list.files(path = params$pacbamDir,
                      full.names = TRUE,
                      recursive = TRUE)

# Now filter it down to just the pileups and sort by even or odd pools
pbFilesPU_even <- vector()
pbFilesPU_odd <- vector()
for (f in 1:length(pbFiles)) {
  if (str_detect(pbFiles[f], "pileup") == TRUE && str_detect(pbFiles[f], "even") == TRUE) {
    pbFilesPU_even <- append(pbFilesPU_even, pbFiles[f])
  } else {
    if (str_detect(pbFiles[f], "pileup") == TRUE && str_detect(pbFiles[f], "odd") == TRUE) {
      pbFilesPU_odd <- append(pbFilesPU_odd, pbFiles[f])
    }
  }
}

# Read it all in and format
keepers <- tibble()
colnames(keepers) <- c("pos", "cov", "SampleID", "SampleGroup", "Amplicon", "UnifiedScale")
for (r in 1:nrow(ampInfo)) { # this gives row index for ampInfo, i.e. a single amplicon
  # Store some info from ampInfo in convenience variables
  start <- ampInfo[r,]$START
  end <- ampInfo[r,]$END
  pool <- ampInfo[r,]$POOL
  ampID <- ampInfo[r,]$AMP_ID
  # Loop over even and odd pools separately. At some point make a proper function instead of repeating code blocks.
  if (pool == 1) {
    for (f in 1:length(pbFilesPU_odd)) { # this gives the index of a file in the odd list
      tempPU <- read_tsv(pbFilesPU_odd[f]) %>%
                dplyr::filter(pos %in% seq(start, end)) %>%
                dplyr::select(pos, cov) %>%
                dplyr::mutate(SampleID = str_replace(pbFilesPU_odd[f], "^.*/odd/", "")) %>%
                dplyr::mutate(SampleID = str_replace(SampleID, params$pacbamFileSuffix, "")) %>%
                dplyr::mutate(SampleGroup = stringr::str_replace(SampleID, "-A(1|2|3|4|5|6|7|8)$", "")) %>%
                dplyr::mutate(Amplicon = ampID) %>%
                dplyr::arrange(pos)
        tempPU <- dplyr::bind_cols(tempPU, seq(1, nrow(tempPU)))
        colnames(tempPU) <- c("pos", "cov", "SampleID", "SampleGroup", "Amplicon", "UnifiedScale")
        keepers <- bind_rows(keepers, tempPU)
    }
  } else {
    if (pool == 2) {
      for (f in 1:length(pbFilesPU_even)) { # this gives the index of a file in the even list
        tempPU <- read_tsv(pbFilesPU_even[f]) %>%
                  dplyr::filter(pos %in% seq(start, end)) %>%
                  dplyr::select(pos, cov) %>%
                  dplyr::mutate(SampleID = str_replace(pbFilesPU_even[f], "^.*/even/", "")) %>%
                  dplyr::mutate(SampleID = str_replace(SampleID, params$pacbamFileSuffix, "")) %>%
                  dplyr::mutate(SampleGroup = stringr::str_replace(SampleID, "-A(1|2|3|4|5|6|7|8)$", "")) %>%
                  dplyr::mutate(Amplicon = ampID) %>%
                  dplyr::arrange(pos)
          tempPU <- dplyr::bind_cols(tempPU, seq(1, nrow(tempPU)))
          colnames(tempPU) <- c("pos", "cov", "SampleID", "SampleGroup", "Amplicon", "UnifiedScale")
          keepers <- bind_rows(keepers, tempPU)
      }
    }
  }
}
```

```{r cov_summary, echo=FALSE, warning=FALSE, message=FALSE}
# Summarize first by SampleID and Amplicon
keepers_sum <- group_by(keepers, SampleID, Amplicon) %>%
               summarise(Coverage.Mean = mean(cov),
                         Coverage.Min = min(cov),
                         Coverage.Max = max(cov)) %>%
               mutate(Mean.Pass = if_else(Coverage.Mean >= params$ampMeanCov, "PASS", "FAIL"),
                      Min.Pass = if_else(Coverage.Min >= params$ampMinCov, "PASS", "FAIL"))

# Now summarize above summary by SampleID
cov_sum <- group_by(keepers_sum, SampleID) %>%
           summarise('Count Amplicons Passing' = sum(Mean.Pass == "PASS" & Min.Pass == "PASS"),
                     'Count Amplicons Failing' = sum(Mean.Pass == "FAIL" | Min.Pass == "FAIL"))

# Add a column with hyperlinks to the detailed report pages.
cov_sum <- mutate(cov_sum, 
                  Report = paste0('<a href="subpages/', 
                                  SampleID, 
                                  '-amplicon-detail.html">report</a>'))

# Divide up the samples and controls
cov_sum_samples <- filter(cov_sum, !str_detect(SampleID, "NC-"))
cov_sum_controls <- filter(cov_sum, str_detect(SampleID, "NC-"))


# Make the summary table pretty
highgood_formatter <- formatter("span", 
                                style = x ~ style("color" = ifelse(x >= params$ampMinNPass, 
                                                                   "green",
                                                                ifelse(x < params$ampMinNPass, 
                                                                       "red", 
                                                                       "gray")),
                                                  "font-weight" = ifelse(x >= params$ampMinNPass, 
                                                                         "plain",
                                                                ifelse(x < params$ampMinNPass, 
                                                                       "bold", 
                                                                       "italic"))
                                ))

lowgood_formatter <- formatter("span", 
                                style = x ~ style("color" = ifelse(x <= params$ampMaxNFail, 
                                                                   "green",
                                                                ifelse(x > params$ampMaxNFail, 
                                                                       "red", 
                                                                       "gray")),
                                                  "font-weight" = ifelse(x <= params$ampMaxNFail, 
                                                                         "plain",
                                                                ifelse(x > params$ampMaxNFail, 
                                                                       "bold", 
                                                                       "italic"))
                                ))
formattable(cov_sum_samples, list(
  'Count Amplicons Passing' = highgood_formatter,
  'Count Amplicons Failing' = lowgood_formatter
))

formattable(cov_sum_controls, list(
  'Count Amplicons Passing' = lowgood_formatter,
  'Count Amplicons Failing' = highgood_formatter
))
```

```{r spawn, include=FALSE}
#echo=FALSE, results='asis', message=FALSE, warning=FALSE}
for (s in 1:nrow(cov_sum)) {
  rmarkdown::render(input = "report/temp/ampliconDetailTemplate.Rmd", 
                    output_file = paste0(cov_sum[s,]$SampleID, "-amplicon-detail.html"), 
                    output_dir = file.path("report", "subpages"),
                    params = list(covTable = filter(keepers, 
                                                    SampleID == cov_sum[s,]$SampleID),
                                  sampleID = cov_sum[s,]$SampleID,
                                  passfailTab = filter(keepers_sum, 
                                                       SampleID == cov_sum[s,]$SampleID)),
                    envir = new.env())
}

# for testing
# rmarkdown::render(input = "ref_docs/ampliconDetailTemplate.Rmd", 
#                     output_file = paste0("3002228466-ZZYGJK71-A6", "-amplicon-detail.html"), 
#                     params = list(covTable = filter(keepers, 
#                                                     SampleID == "3002228466-ZZYGJK71-A6"),
#                                   sampleID = "3002228466-ZZYGJK71-A6",
#                                   passfailTab = filter(keepers_sum, 
#                                                        SampleID == "3002228466-ZZYGJK71-A6")),
#                     envir = new.env())

```
