---
title: "Amplicon Coverage Detailed Report"
params:
    covTable: null
    sampleID: null
    passfailTab: null
---

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(formattable)
library(DT)
library(dygraphs)
```
#### Sample ID: `r params$sampleID`

```{r ampPF, echo=FALSE, results='asis', eval=TRUE}
# Parse data passed from sampleCov.Rmd on amplicon pass/fails
# Number amplicons passing QC
nPass <- nrow(filter(params$passfailTab, Mean.Pass == "PASS" & Min.Pass == "PASS"))
# Amplicon ID numbers for those that failed QC (mean cov <100, min cov <30)
fails <- filter(params$passfailTab, Mean.Pass == "FAIL" | Min.Pass == "FAIL")$Amplicon
```
`r nPass` amplicons passed QC filters for sample `r params$sampleID`.  
`r length(fails)` amplicons failed QC, including:
<br>

```{r ampFails, echo=FALSE, results='asis', eval=TRUE}
# Generates the bulleted list of failed amplicons with hyperlinks to appropriate plots
if (length(fails) > 0) {
  outlist <- lapply(fails, function(x) paste0('* <a href="#amp', x, '">', x, '</a>\n'))
  for(x in outlist) {cat(x)}
} else {
  cat("NA")
}
```

***
_Using interactive graphs:_  
* Mousing over the plot lines causes the plot to display precise reference genome position and coverage in the upper right of the plot.
* Click and drag to zoom in on a section of a plot.
* Double click to zoom back out.  
***

```{r cov_tab, echo=FALSE, message=FALSE}
# Remove unneeded columns from coverage table passed by sampleCov.Rmd
covTab <- select(params$covTable, pos, cov, Amplicon)
```

```{r all_plots, echo=FALSE, message=FALSE}
# Generates all of the interactive amplicon plots
manyPlots <- lapply(seq(1, 98), function(x) dygraph(dplyr::filter(covTab, Amplicon == x) %>% 
                                                    select(-Amplicon), 
                                                    main = paste0('<h2 id="amp', 
                                                                    x, 
                                                                    '">Amplicon ', 
                                                                    x,
                                                                    '</h2>'),
                                                    ylab = "Coverage Depth (bases)",
                                                    xlab = "Position within the Reference Genome"))
htmltools::tagList(manyPlots)
#dygraph(dplyr::filter(inTable, Amplicon == 1))
```

